Deterministic Scheduling of Periodic Messages in a Network

### 2017-07-18 article/article.tex
avant bosser

\todo{citation [7] pour les reseaux points a points ?}
 In this article, we study mechanisms to deal with the latency and periodicity constraints in the network located between the BUUs and the RRHs called fronthaul.
 Statistical multiplexing even with a large bandwidth does not comply with the latency requirements. Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits. Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches. This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations. Here we propose to use a deterministic approach to schedule our periodic messages. This approach has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}. Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}. The aim is to operate a C-RAN on a low-cost shared switched network.

@@

    In this section, we first try to understand what is the best choice of order for the first stage of the algorithm.
    We fix the number of routes to $8$ to make comparisons with the results of Section~\ref{sec:exp_PAZL} easier. 
    We draw uniformly the weights of the arcs between $0$ and $20000$ slots.
    For a given routed network, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
    Hence, for a routed network choosing the margin or $T_{max}$ is the same, but since we will consider many networks 
    whith different longest route's size, it will be more meaningful to set the margin rather than $T_{max}$.
    In fact the margin represents the latency imposed by the communication process without taking into account the physical length of the network which cannot be changed. In our experiments the margin range from  $0$ to $3000$ slots.
   We look at two different regimes: we take a period equal to $1,05n\tau$ to represent a very loaded network
   and $1,5n\tau$ for a mildly loaded network. Choosing a larger period is not relevant since then we know how to solve the problem even without waiting times as shown in Section~\ref{sec:exp_PAZL}. We represent the success rate with regards to the margin, for the five kind of orders using the Greedy algorithm for the second stage, computed over $10000$ random star topologies. Note that for the random order, we compute $1000$ random orders and count it as a success as soon as there is a solution for one order.

@@

     The random order is the best by far. When the load is not too high ($P = 30000$) there is always a solution with margin $0$.
     Note that, when disallowing waiting times, there were instances without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the PALL problem. We now want to compare the performances of the three different algorithms used in the second stage. Since GD already showed excellent results on mild loads, it is more interesting to focus on the behavior of the algorithms on high load. Moreover, we will use $1000$ random orders for the first stage as it gives the best results. The following experiment is realized on routed networks with $8$ routes, weights of the arcs drawn between $0$ and $20000$ and with a period of $21000$.  We represent the success rate with regards to the margin, for the three algorithms computed over $10000$ random star topologies.

>>>>

 In this article, we study mechanisms to deal with the latency and periodicity constraints in the network located between the BUUs and the RRHs called fronthaul.
 Statistical multiplexing even with a large bandwidth does not comply with the latency requirements. Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits. Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches. This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations. Here we propose to use a deterministic approach to schedule our periodic messages. This approach has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}. Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}. The aim is to operate a C-RAN on a low-cost shared switched network.

@@

    In this section, we first try to understand what is the best choice of order for the first stage of the algorithm.
    We fix the number of routes to $8$ to make comparisons with the results of Section~\ref{sec:exp_PAZL} easier. 
    We draw uniformly the weights of the arcs between $0$ and $20000$ slots.
    For a given routed network, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
    Hence, for a routed network choosing the margin or $T_{max}$ is the same, but since we will consider many networks 
    whith different longest route's size, it will be more meaningful to set the margin rather than $T_{max}$.
    In fact the margin represents the latency imposed by the communication process without taking into account the physical length of the network which cannot be changed. In our experiments the margin range from  $0$ to $3000$ slots.
   We look at two different regimes: we take a period equal to $1,05n\tau$ to represent a very loaded network
   and $1,5n\tau$ for a mildly loaded network. Choosing a larger period is not relevant since then we know how to solve the problem even without waiting times as shown in Section~\ref{sec:exp_PAZL}. We represent the success rate with regards to the margin, for the five kind of orders using the Greedy algorithm for the second stage, computed over $10000$ random star routed networks. Note that for the random order, we compute $1000$ random orders and count it as a success as soon as there is a solution for one order.

@@

     The random order is the best by far. When the load is not too high ($P = 30000$) there is always a solution with margin $0$.
     Note that, when disallowing waiting times, there were instances without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the PALL problem. We now want to compare the performances of the three different algorithms used in the second stage. Since GD already showed excellent results on mild loads, it is more interesting to focus on the behavior of the algorithms on high load. Moreover, we will use $1000$ random orders for the first stage as it gives the best results. The following experiment is realized on routed networks with $8$ routes, weights of the arcs drawn between $0$ and $20000$ and with a period of $21000$.  We represent the success rate with regards to the margin, for the three algorithms computed over $10000$ random star routed networks.
